\documentclass[12pt,fleqn]{article}

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'tex/git and can be run from
% the command line in the project's top directory via:
%
% $ tex/git
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

\IfFileExists{./VERSION.tex}{\input{VERSION}}{%
\providecommand\VERSION{\today}}

\input{tex/setup}
\input{tex/macros}

\begin{document}

\noindent%
Hi Matias,

Thank you for your helpful comments. We have made the requested changes. Overall,
for this version of the paper, we have changed the bootstrap method from the
residual bootstrap to the wild bootstrap. We have also updated the simulations
to include DGPs featuring heteroskedasticity. We believe that the residual
bootstrap used in the previous version is theoretically correct even under
heteroskedastcity as long as the conditional variance is assumed to be smooth in
a neighborhood around the cutoff point, since the residual bootstrap we initially
proposed only resampled from that neighborhood, but we agree that in practice
the wild bootstrap is likely to be more accurate and can accommodate forms of
conditional heteroskedasticity that the residual bootstrap can not.

We have also relaxed the ``uniform kernel'' requirement and allow other kernels
that are popular in practice. The title of the paper has been updated to reflect
that change.

The first referee expressed concern about the possible computational complexity of
using an iterated bootstrap to produce confidence intervals. This is much less
of an issue than it appears, because many of the matrix calculations can be
computed once and then reused in the bootstrap replications. (Any calculation
that does not involve $Y$ can be reused.) Each bootstrap replication only
requires a small number of matrix-vector multiplications which can be completed
very quickly. We have added a short section after Algorithm 2 that explains
this implementation detail, and we have also provided open source R code that
implements the procedure efficiently.

Finally, the mathematical appendix defines more notation explicitly and
summarizes several convergence results from Calonico, Cattaneo, and Titiunik
(2014) that are referenced in the proofs and we have made some small additional
changes that the referees suggested.

The replies to the referees give more details on some of the specific
changes made to the paper. Thank you for giving us the opportunity to revise
the paper.

\strut

\noindent%
Best,

\noindent%
Ot\'avio Bartalotti, Gray Calhoun, and Yang He

\end{document}